MP MetaAnalysis

### 2018-10-10 Paper_Analyses.Rmd
updated methods/results

---
title: "MP MetaAnalysis"
author: "Christina Bergmann"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

### Load libraries
library(tidyverse)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(ggplot2)
library(wesanderson)
library(grid)
library(gridExtra)

@@

@@

db_ET$lang_family = ifelse(db_ET$native_lang=="American English" | db_ET$native_lang=="British English" | db_ET$native_lang=="Dutch" |
db_ET$native_lang=="Danish" | db_ET$native_lang=="Swedish" |
db_ET$native_lang=="English" | db_ET$native_lang=="German", "Germanic", ifelse(db_ET$native_lang == "French" | db_ET$native_lang == "Catalan" | db_ET$native_lang == "Spanish" | db_ET$native_lang == "Catalan-Spanish" | db_ET$native_lang == "Swiss French", 
                                "Romanic", "Sino-Tibetian"))

@@

The present meta-analysis was conducted with maximal transparency and reproducibility in mind. To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014). In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials. (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).

## Study Selection
We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. We screened the 398 items, removing 99 duplicate items. We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; 5) the stimuli were auditory speech. The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.

@@

@@

The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age. The results are clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity. This did not change with development. Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop. This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity. In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.

Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages. To examine this possibility, we include an exploratory analysis of whether different moderators and experimental design features were included at different ages. We return to this possibility after the Moderator Analyses.

>>>>

---
title: "MP MetaAnalysis"
author: "Christina Bergmann and Katie Von Holzen"
date: '`r format(Sys.Date(), "%d %B, %Y")`'
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

### Load libraries
library(tidyverse)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(ggplot2)
library(wesanderson)
library(grid)
library(gridExtra)
library(xtable)
library(schoRsch)
library(multcomp)

@@

# function for creating 1 line paired t.test results
t.xtable <- function(x) as.data.frame(xtable(
  t_out(toutput=x, n.equal = TRUE, welch.df.exact = TRUE, welch.n = NA,
        d.corr = TRUE, print = TRUE)
))

cur_dir <- getwd()

@@

db_ET$lang_family = ifelse(db_ET$native_lang=="American English" | db_ET$native_lang=="British English" | db_ET$native_lang=="Dutch" |
db_ET$native_lang=="Danish" | db_ET$native_lang=="Swedish" |
db_ET$native_lang=="English" | db_ET$native_lang=="German", "Germanic", ifelse(db_ET$native_lang == "French" | db_ET$native_lang == "Catalan" | db_ET$native_lang == "Spanish" | db_ET$native_lang == "Catalan-Spanish" | db_ET$native_lang == "Swiss French", 
                                "Romance", "Sino-Tibetian"))

@@

The present meta-analysis was conducted with maximal transparency and reproducibility in mind. To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014). In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009). Figure X plots our PRISMA flowchart.

![Figure X. PRISMA Flowchart.] (figures/PRISMA_MA_Mispronunciation.png)

## Study Selection

```{r SummaryTable, echo = FALSE}

dat_st <- dat

dat_st$object_pair <- ifelse(dat_st$object_pair == "familiar_familiar", "Familiar", "Unfamiliar")

Sum_table <- dat_st %>%
      group_by(short_cite) %>% 
      summarise(Ages_Tested_months = paste(unique(trunc(mean_age_1/30.34)), collapse=', '),
                Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comprehension/Production",
                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comprehension", "Production"))),
                Number_of_Features = paste(unique(n_feature), collapse=', '),
                Distractor_Familiarity = paste(unique(object_pair), collapse=', '),
                Distractor_Overlap = paste(unique(distractor_overlap), collapse=', '),
                Mispronunciation_Position = paste(unique(mispron_location), collapse=', '),
                Mispronunciation_type = paste(unique(type_feature), collapse=', '))

kable(Sum_table)

[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. We screened the 398 items, removing 99 duplicate items. We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; 5) the stimuli were auditory speech. The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.

@@

[KATIE] I DON'T KNOW HOW TO INTERPRET THESE RESULTS... THE FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT MEANINGFUL?

@@

The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age. The results are clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity. This did not change with development. Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop. This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.

[KATIE] CAN A CONCLUSION BE DRAWN FROM THE VOCABULARY RESULTS? IF SO, THIS IS THE PARAGRAPH

In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.

Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages. To examine this possibility, we include an exploratory analysis of whether different moderators and experimental design features were included at different ages, in addition to investigating the role that these moderators play in mispronunciation sensitivity.

## Moderator Analyses

### Size of mispronunciation

```{r NFeatures_demographics}

dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

nfeature_info <- dat.f %>%
  group_by(n_feature) %>%
  summarize(n_exp_conditions =  n())

To assess whether the number of features changed modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes. We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent. The analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations. Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity (White & Aslin, 2008; Mani & Plunkett 2011).

```{r NFeatures}

dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat.f, random = ~collapse | short_cite)

 sum_eff <- coef(summary(rma_NFeatures))[2,]

To understand the relationship between size of mispronunciation and mispronunciation sensitivity, we  evaluated the effect size Hedges’ *g* with number of features changed as a moderator. The moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, p `r psig(rma_NFeatures$QMp)`.  Hedges’ *g* for number of features changed was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that as the number of features changed increased, the effect size Hedges’ g significantly decreased (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`). We plot this relationship in Figure X. This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.

```{r PlotFeatEffect, echo = FALSE}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "1-feature",
                         ifelse(dat_f$n_feature == 2, "2-feature",
                                ifelse(dat_f$n_feature == 3, "3-feature",
                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))

dat_f <- subset(dat_f, feat_cat != "none")

dat_f$Features_changed <- factor(dat_f$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))

p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Figure_3_Number_of_Features.jpg", 
       width = 500, height = 300, units = "px")

```{r NFeatures_age}

dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat.f, random = ~collapse | short_cite)

 sum_eff <- coef(summary(rma_NFeatures))[4,]

Although we did not have any specific predictions about the relationship between infant age and the impact of number of features changed on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship. When age was also included as a moderator, the moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, p `r psig(rma_NFeatures$QMp)`, but the interaction between age and number of features changed was not significant, $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`). This suggests that there is no relationship between infant age the impact of number of features changed on mispronunciation sensitivity.

```{r NFeatures_subset}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

nfeature_ages <- dat.f %>%
  group_by(n_feature) %>%
  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
            max_age = r2(max(mean_age_1, na.rm=TRUE)),
            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))

mf <- subset(dat_f, n_feature == "3")
min_age <- min(mf$mean_age_1)
max_age <- max(mf$mean_age_1)

dat_fage= dat_f%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_fage, random = ~collapse | short_cite)

 sum_eff1 <- coef(summary(rma_NFeatures_agesub))[2,]

rma_AGENFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat_fage, random = ~collapse | short_cite)

 sum_eff2 <- coef(summary(rma_AGENFeatures_agesub))[4,]

Although all papers included in the dataset also included correct pronunciations, not all papers included all three types of feature changes (i.e. 1-3). The age range for each type of number of features changed was `r with(nfeature_ages, min_age[n_feature == 1])` - `r with(nfeature_ages, max_age[n_feature == 1])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 1])`) for 1-feature mispronunciations, `r with(nfeature_ages, min_age[n_feature == 2])` - `r with(nfeature_ages, max_age[n_feature == 2])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 2])`) for 2-feature mispronunciations, and `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 3])`) for 3-feature mispronunciations. Focusing on the ages where all three numbers of features changed were tested (i.e. `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days), however, did not change the pattern of results.

[KATIE] DOES THE ABOVE PARAGRAPH NEED MORE MOTIVATION? SHOULD IT EVEN BE INCLUDED?

### Distractor familiarity

```{r DistractorType_misp}

rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)

sum_eff <- coef(summary(rma_Distractor))[4,]

We next assessed whether distractor familiarity has an impact on the size of mispronunciation sensitivity. First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images that were paired with either a familiar or an unfamiliar distractor image. The moderator test was not significant QM(`r r2(rma_Distractor_MP$m)`) = `r r2(rma_Distractor_MP$QM)`, p `r psig(rma_Distractor_MP$QMp)`. This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object. We next assessed whether distractor familiarity was related to mispronunciation sensitivity. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, QM(`r r2(rma_Distractor$m)`) = `r r2(rma_Distractor$QM)`, p `r psig(rma_Distractor$QMp)`, but the interaction between distractor familiarity and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`). These results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.

```{r PlotDistFamEffect_NoAge}

dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")

p <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
  geom_boxplot() + 
  facet_grid(.~dist_code) +
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Figure_4Distractor_fam.jpg", 
       width = 500, height = 300, units = "px")

```{r DistractorTypeAge}

rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)

sum_eff <- coef(summary(rma_DistractorAge))[4,]

rma_DistractorAgeMS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)

#summary(rma_DistractorAgeMS)

sum_eff1 <- coef(summary(rma_DistractorAgeMS))[8,]
sum_eff2 <- coef(summary(rma_DistractorAgeMS))[7,]

We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar. For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_DistractorAge$m)`) = `r r2(rma_DistractorAge$QM)`, p `r psig(rma_DistractorAge$QMp)`. This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object, regardless of their age. We next assessed whether the relationship between distractor familiarity and mispronunciation sensitivity was modulated by age. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators. The moderator test was significant, QM(`r r2(rma_DistractorAgeMS$m)`) = `r r2(rma_DistractorAgeMS$QM)`, p `r psig(rma_DistractorAgeMS$QMp)`. Although the three-way-interaction between condition, distractor familiarity, and age was not significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), here the interaction between condition and distractor familiarity was significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`).

[KATIE] WHAT DOES IT MEAN THAT IN THIS LAST TEST THERE WAS AN INTERACTION BETWEEN CONDITION AND DISTRACTOR FAMILIARITY, WHEN AGE WAS INCLUDED AS A MODERATOR? DOES THAT MEAN THAT AGE IS CONTROLLED FOR? UNDERSTANDING THIS WILL HELP ME FORMULATE THE CONCLUSION SENTENCE AND MOTIVATE THE NEXT SET OF ANALYSES.

```{r DistractorTypeAgeRangeSubset}

object_pair_ages <- dat %>%
  group_by(object_pair) %>%
  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
            max_age = r2(max(mean_age_1, na.rm=TRUE)),
            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))

fn <- subset(dat, object_pair=="familiar_novel")

ff <- subset(dat, object_pair=="familiar_familiar")

age_diff_dist <- t.xtable(t.test(fn$mean_age_1, ff$mean_age_1, paired = F))

#t.test(fn$mean_age_1, ff$mean_age_1)

opa <- as.data.frame(object_pair_ages)
min_age <- max(opa$min_age)
max_age <- min(opa$max_age)

dat_age_MP= db_ET_MP%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)

#summary(rma_Distractor_MP)

sum_eff <- round(coef(summary(rma_Distractor_MP))[2,], 2)

# misp sensitivity
dat_age= dat%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_Distractor_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat_age, random = ~ collapse | short_cite)

#summary(rma_Distractor_MS)

sum_eff <- coef(summary(rma_Distractor_MS))[2,]

Although we anticipated that older children may be more impacted by the presence of a unfamiliar compared to familiar distractor image, we found that age and distractor familiarity did not impact mispronunciation sensitivity. Inspection of the ages tested using different kinds of distractors, however, revealed differences. Infants tested using a familiar distractor were younger (M = 588.76 days, SD = 136.47, range = 207.8 - 768 days) than those infants tested using an unfamiliar distractor (M = 678.85 days, SD = 115.47, range = 544.48 - 920.2 days), which a two-sample t-test revealed to be a significant difference, t(153.83) = 5.30, p < .0001.

[KATIE] SO, IS IT OKAY TO DO THE AGE SUBSET ANALYSIS AFTER THIS? SOMETHING LIKE "TO ENSURE THAT THE LACK OF A DIFFERENCE WASN'T DUE TO THE DIFFERENCE IN AGES OF INFANTS TESTED WITH DIFFERENT TYPES OF DISTRACTORS, WE ANALYZED A SUBSET OF PAPERS THAT TESTED AGES WHERE BOTH FAMILIAR AND UNFAMILIAR DISTRACTORS WERE USED." IN THE SUBSET ANALYSIS, FOR MISP SENSITIVITY, THERE IS A SIGNIFICANT INTERACTION BETWEEN DISTRACTOR FAMILIARITY AND CONDITION.

### Phonological overlap between target and distractor

```{r DistractorOverlap_descrip}

dist_overlap_info <- dat %>%
  group_by(distractor_overlap) %>%
  summarize(n_exp_conditions =  n())

To assess whether phonological overlap between the target and distractor image labels has an impact on the size of mispronunciation sensitivity, we examined the meta-analytic effect for object identification in response to mispronunciations and mispronunciation sensitivity when the target-distractor pairs either shared the same onset phoneme, had no overlap, or where the distractor was an unfamiliar object. We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`) or coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`). The analysis was therefore based on a subset of the overall dataset, with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` experimental conditions containing onset phoneme overlap between the target and distractor, `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor, and `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])` for targets paired with unfamiliar distractor images. There were therfore three possibilities for distractor overlap: onset phoneme overlap, no overlap, and an unfamiliar distractor. In our analysis, we were interested in the difference between overlap and lack of overlap; therefore, experimental conditions containing onset phoneme overlap were coded as the reference condition and compared with responses to experimental conditions with no overlap or an unfamiliar distractor separately.

[KATIE] CAN YOU CHECK THE WAY THAT I WROTE THE LAST SENTENCE?

```{r DistractorOverlap}
db_ET_MPo = db_ET_MP %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)

#summary(rma_DistractorOverlap)

db_ET_MPo_MS = dat %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

db_ET_MPo_MS$distractor_overlap <- factor(db_ET_MPo_MS$distractor_overlap, levels = c("onset", "no", "novel"))

rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = ~ collapse | short_cite)

#summary(rma_DistractorOverlapMS)

sum_eff1 <- coef(summary(rma_DistractorOverlapMS))[5,]
sum_eff2 <- coef(summary(rma_DistractorOverlapMS))[6,]

Regarding object identification in response to mispronunciations, when distractor overlap was included as a moderator, the moderator test was not significant QM(`r r2(rma_DistractorOverlap$m)`) = `r r2(rma_DistractorOverlap$QM)`, p `r psig(rma_DistractorOverlap$QMp)`. This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with a distractor image that contained overlap on the onset phoneme or no overlap with the target word, or was an unfamiliar object. We next assessed whether target-distractor overlap was related to mispronunciation sensitivity. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, QM(`r r2(rma_DistractorOverlapMS$m)`) = `r r2(rma_DistractorOverlapMS$QM)`, p `r psig(rma_DistractorOverlapMS$QMp)`. The interaction between condition and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap. The interaction between condition and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`), suggesting that mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object. This can be seen in Figure X.

```{r PlotDistOverlapEffect}

db_ET_MPo = dat %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))

db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")

p <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
  facet_grid(.~distractor_overlap)+
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Figure_5_Distractor_overlap.jpg", 
       width = 500, height = 300, units = "px")

```{r DistractorOverlap_age}

# object recognition
db_ET_MPo = db_ET_MP %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))

rma_DistractorOverlap_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)

# mispronunciation sensitivity
dat_MPo = dat %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

dat_MPo$distractor_overlap <- factor(dat_MPo$distractor_overlap, levels = c("onset", "no", "novel"))

rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ collapse | short_cite)

#summary(rma_DistractorOverlap_age_MS)

sum_eff1 <- coef(summary(rma_DistractorOverlap_age_MS))[11,]
sum_eff2 <- coef(summary(rma_DistractorOverlap_age_MS))[12,]

Although we did not have any specific predictions about the relationship between infant age and the impact of distractor overlap on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship. First, for object recognition in response to mispronunciations, when age in addition to distractor overlap was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_DistractorOverlap_age$m)`) = `r r2(rma_DistractorOverlap_age$QM)`, p `r psig(rma_DistractorOverlap_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for the three types of overlap, regardless of infant age. We next assessed whether the relationship between distractor overlap and mispronunciation sensitivity was modulated by age. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators. The moderator test was significant, QM(`r r2(rma_DistractorOverlap_age_MS$m)`) = `r r2(rma_DistractorOverlap_age_MS$QM)`, p `r psig(rma_DistractorOverlap_age_MS$QMp)`. The interaction between age, condition, and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`). As can be seen in Figure X, the difference between correct pronunciations and mispronunciations (mispronunciation sensitivity) stays steady across infant ages for both target words paired with distractors containing onset overlap with the target word as well as distractors containing no overlap. As infants aged, however, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas for overall recognition decreased for target-distractor pairs containing no overlap. The interaction between age, condition, and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`). As can also be seen in Figure X, mispronunciation sensitivity for target words paired with unfamiliar distractors decreased with age, while it remained steady across a similar range of ages for target words paired with distractors containing onset overlap with the target word.

```{r PlotDistOverlap_cond_age}

db_ET_MPo = dat %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))

db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")

p <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
    facet_grid(.~distractor_overlap)+
  geom_point(aes(size = weights_g),show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Figure_6_Distractor_overlap_age.jpg", 
       width = 500, height = 300, units = "px")

### Position of mispronunciation

```{r Location_descrip}

misp_location_info <- dat %>%
  group_by(mispron_location) %>%
  summarize(n_exp_conditions =  n())
